%!TEX root = Slic3r-Manual.tex
\subsection{\texttt{Slic3r Support}} % (fold)
\label{sec:slic3r_support}

\index{community support}
\index{Freenode}
\index{IRC}
\index{RepRap}
\index{forums}
\index{website}
\index{blog}

A variety of resources are available to provide support for Slic3r.
\subsubsection{\texttt{Wiki and FAQ}} % (fold)
\label{sub:wiki_and_faq}
The wiki provides up-to-date documentation, and a FAQ subsection which may help resolve any queries or issues.
\begin{itemize}
    \item \texttt{https://github.com/alexrj/Slic3r/wiki/Documentation}
    \item \texttt{https://github.com/alexrj/Slic3r/wiki/FAQ}
\end{itemize}
% subsubsection wiki_and_faq (end)

\subsubsection{\texttt{Blog}} % (fold)
\label{sub:blog}
The Slic3r blog contains tips, hints, and advice.
\begin{itemize}
    \item \texttt{http://slic3r.org/blog}
\end{itemize}
% subsubsection blog (end)

\subsubsection{\texttt{IRC}} % (fold)
\label{sub:irc}

Found on the \texttt{irc.freenode.net} server, the following chat rooms are often filled with people who can provide real-time help:
\begin{itemize}
\item \texttt{\#reprap}: Highly active community of the RepRap project with many users of Slic3r.
\item \texttt{\#slic3r}: Slic3r chat room where Slic3r developers and users can provide help.
\end{itemize}

% subsubsection irc (end)

\subsubsection{\texttt{RepRap.org Forum}} % (fold)
\label{sub:reprap_org_forum}


The RepRap forums contain a dedicated forum for Slic3r.
\begin{itemize}
    \item \texttt{forums.reprap.org/list.php?263}
\end{itemize}

% subsubsection reprap_org_forum (end)

\subsubsection{\texttt{Issue Tracker}} % (fold)
\label{sub:issue_tracker}

If you find a bug in the software, then raise the issue in the project issue tracker.

\begin{itemize}
    \item \texttt{github.com/alexrj/Slic3r/issues}
\end{itemize}

\textbf{Please} take the time to read through the existing issues to see whether the problem has already been submitted.  Also make sure that the problem is a bug in the application; do not submit support related questions here.
If the bug appears to be unreported then please read the bug report guide before submitting: \texttt{http://git.io/11Hy\_w}.
% subsubsection issue_tracker (end)

% subsection slic3r_support (end)
